---
title: "Q1: Another Random Sample"
output: 
  github_document:
    toc: false
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = FALSE)
library(tidyverse)
theme_set(theme_classic(base_size = 14))
```

DeShawn is a lawyer. He works at a gigantic law firm with 100,000 lawyers. He was curious about the commute times of lawyers at his company, so he randomly selected 1,000 lawyers, sent them a survey asking them how long it takes them to get to work, and graphed the results:

```{r}
set.seed(2)

make_commute_time_data <- function(mean){
   data_frame(
      commute_time = rnorm(1000, mean, 10) 
   ) %>% 
   mutate(
      commute_time = ifelse(commute_time <= 5, 5, commute_time)
   )
}

original_sample <- make_commute_time_data(mean = 20)

original_sample %>% 
   ggplot(aes(x = commute_time)) +
   geom_histogram(bins = 40) +
   labs(
      x = "commute time (in minutes)",
      y = "Count",
      title = "Commute time for a random sample of lawyers"
   )
```

DeShawn then took *another* random sample of 1000 lawyers at his company, sent them the new survey, and graphed the new results.

**Which of the following graphs is most likely his new results?**

```{r}
bind_rows(
   original_sample %>% mutate(option = "A"),
   make_commute_time_data(mean = 40) %>% mutate(option = "B"),
   make_commute_time_data(mean = 20) %>% mutate(option = "C"),
   data_frame(commute_time = rlnorm(1000, log(25), log(2))) %>% 
      mutate(
         commute_time = ifelse(commute_time <= 5, 5, commute_time),
         option = "D"
      )
) %>% 
   ggplot(aes(x = commute_time)) +
   geom_histogram(bins = 40) +
   facet_wrap(~ option, scales = "free") +
   labs(
      x = "Commute time (in minutes)",
      y = "Count",
      title = expression(paste("Commute time for ", italic("another"), " random sample of lawyers"))
   )
```